From Object Classification to Naming: Modeling Entry-level Names for Real-world Objects

### 2019-12-09 papers/ACL2020/analysis.tex
changes in sec 3.1
[ACL2020] analysis

\begin{table*}[t]
\centering
	\small
\begin{tabular}{ll||rr|rrr}
\toprule
&  & \multicolumn{2}{c|}{Correct} & \multicolumn{3}{c}{Incorrect}\\
                         model &  gt &  hit &  valid &  human-like &  related &  off \\
\midrule
       FRCNN$_{\text{VG1600}}$ &  VG & 74.8 &     13.7 &         5.3 &      1.7 &    4.5 \\
        FRCNN$_{\text{MN442}}$ &  VG & 71.1 &     13.6 &         5.3 &      2.6 &    7.4 \\
        \midrule
 FRCNN$_{\text{VG1600--VGMN}}$ &  MN & 80.7 &      9.0 &         3.7 &      3.4 &    3.3 \\
         \midrule
     ResNet101$_{\text{VGMN}}$ &  VG & 62.8 &     11.6 &         5.2 &     10.3 &   10.1 \\
         ResNet101$_{\text{MN442}}$ &  VG & 63.8 &     11.9 &         5.7 &      8.8 &    9.9 \\
     ResNet101$_{\text{VGMN}}$ &  MN & 68.7 &      9.9 &         5.5 &      7.7 &    8.2 \\
    ResNet101$_{\text{MN442}}$ &  MN & 69.7 &      9.9 &         5.9 &      7.0 &    7.6 \\
\bottomrule
\end{tabular}

\caption{Model results for different categories of errors} \label{tab:humanlike}
\end{table*}

\begin{table*}[t]
	\centering
	\small
\begin{tabular}{ll||c|cccc|c}
	\toprule
	  &  & Hit & \multicolumn{4}{c|}{Human-like} & Off \\
	Model &  GT &  & SameObject &  OtherObject &  Low Count &  Related &   \\
	\midrule
	FRCNN--VG1600&VG &         74.8 &                13.7 &                  2.9 &              2.4 &              1.7 &          4.5 \\
	FRCNN--MN442&VG &         71.1 &                13.6 &                  3.4 &              2.0 &              2.6 &          7.4 \\
	\midrule
	FRCNN--VG1600--VGMN&MN &         80.7 &                 9.0 &                  2.0 &              1.8 &              3.4 &          3.3 \\
	\midrule
	ResNet101--VGMN&VG &         62.8 &                11.6 &                  2.1 &              3.2 &             10.3 &         10.1 \\
	ResNet101--MN442&VG &         63.8 &                11.9 &                  2.4 &              3.3 &              8.8 &          9.9 \\
	ResNet101--VGMN&MN &         68.7 &                 9.9 &                  3.0 &              2.5 &              7.7 &          8.2 \\
	ResNet101--MN442&MN &         69.7 &                 9.9 &                  3.2 &              2.7 &              7.0 &          7.6 \\

	\bottomrule
\end{tabular}
\end{table*}

>>>>

\iffalse
\begin{table*}[t]
\centering
	\small
\begin{tabular}{ll||rr|rrr}
\toprule
&  & \multicolumn{2}{c|}{Correct} & \multicolumn{3}{c}{Incorrect}\\
                         model &  gt &  hit &  valid &  human-like &  related &  off \\
\midrule
       FRCNN$_{\text{VG1600}}$ &  VG & 74.8 &     13.7 &         5.3 &      1.7 &    4.5 \\
        FRCNN$_{\text{MN442}}$ &  VG & 71.1 &     13.6 &         5.3 &      2.6 &    7.4 \\
        \midrule
 FRCNN$_{\text{VG1600--VGMN}}$ &  MN & 80.7 &      9.0 &         3.7 &      3.4 &    3.3 \\
         \midrule
     ResNet101$_{\text{VGMN}}$ &  VG & 62.8 &     11.6 &         5.2 &     10.3 &   10.1 \\
         ResNet101$_{\text{MN442}}$ &  VG & 63.8 &     11.9 &         5.7 &      8.8 &    9.9 \\
     ResNet101$_{\text{VGMN}}$ &  MN & 68.7 &      9.9 &         5.5 &      7.7 &    8.2 \\
    ResNet101$_{\text{MN442}}$ &  MN & 69.7 &      9.9 &         5.9 &      7.0 &    7.6 \\
\bottomrule
\end{tabular}

\caption{Model results for different categories of errors} \label{tab:humanlike}
\end{table*}
\fi

\begin{table*}[t]
	\centering
	\small
\begin{tabular}{ll||c|cccc|c}
	\toprule
	  &  & Hit & \multicolumn{4}{c|}{Human-like} & Off \\
	Model &  GT &  & SameObject &  OtherObject &  Low Count &  Related &   \\
	\midrule
	FRCNN--VG1600&VG &         74.8 &                13.7 &                  2.9 &              2.4 &              1.7 &          4.5 \\
	FRCNN--MN442&VG &         71.1 &                13.6 &                  3.4 &              2.0 &              2.6 &          7.4 \\
	\midrule
	FRCNN--VG1600--VGMN&MN &         80.7 &                 9.0 &                  2.0 &              1.8 &              3.4 &          3.3 \\
	\midrule
	ResNet101--VGMN&VG &         62.8 &                11.6 &                  2.1 &              3.2 &             10.3 &         10.1 \\
	ResNet101--MN442&VG &         63.8 &                11.9 &                  2.4 &              3.3 &              8.8 &          9.9 \\
	ResNet101--VGMN&MN &         68.7 &                 9.9 &                  3.0 &              2.5 &              7.7 &          8.2 \\
	ResNet101--MN442&MN &         69.7 &                 9.9 &                  3.2 &              2.7 &              7.0 &          7.6 \\	
	\bottomrule
\end{tabular}
\caption{Model results for different categories of errors. \label{tab:humanlike}}
\end{table*}

\begin{table*}[t]
	\centering
	\small
\begin{tabular}{ll|c@{~}c@{~}c@{~}c}
	\toprule
	{Model} &  GT & visual &  linguistic &  box &  other \\
	\midrule
	FRCNN--VG1600 & VG &             4.3 &                 0.0 &                  95.7 &            0.0 \\
	FRCNN--MN442 & VG &             3.4 &                 0.0 &                  96.6 &            0.0 \\
	\midrule
	FRCNN--VG1600--VGMN & MN &             6.7 &                 0.0 &                  93.3 &            0.0 \\
	\midrule
	ResNet101--VGMN & VG &             5.6 &                 0.0 &                  94.4 &            0.0 \\
	ResNet101--MN442 & VG &             4.8 &                 0.0 &                  95.2 &            0.0 \\
	ResNet101--VGMN & MN &             3.1 &                 0.0 &                  96.9 &            0.0 \\
	ResNet101--MN442 & MN &             3.0 &                 0.0 &                  97.0 &            0.0 \\
	\bottomrule
\end{tabular}
\caption{Break-down of the instances (in \%) for which the models predicted an \textit{inadequate} name according to the type of inadequacy.  \label{tab:exp_inadequacy}}
\end{table*}

\paragraph{Why May Models Predict Inadequate Names?}
In Table~\ref{tab:exp_inadequacy} we focus on the predicted names that are in \mn for the corresponding objects, but judged as inadequate (i.e.,~adequacy score$<0.5$). 
Most of the inadequate object name predictions are related to an inaccurate bounding box. 
The overall best FRCNN$_{\text{VG1600--VGMN}}$ model has the smallest proportion of box errors, and hence, the least \textit{visual} (i.e.,~the object is difficult to interpret) inadequate name predictions. 
\cs{remove next couple of sentences? it's very assumptive}
This may be due to it using features pre-trained towards object detection (i.e.,~localization), but then being optimized towards \mn entry-level names. 
And the ResNet101-based models, which use features that were pre-trained towards image classification (i.e.,~categorizing the salient object in an image (region)), make slightly more visual errors when being optimized on \vg ground truth labels than their \mn ground truth counterparts.

None of the models predicted an inadequate name that was a linguistic, or any other error. 
The results show that the models make similar mistakes to humans (problems in identifying or recognizing the target object) when being faced with data that was collected with a task setup that approximates human behavior, such as \mn.  
It HERAUSLOCKEN also, though, the limitations of using annotated datasets such as \mn as approximation for human behavior on object naming )or related tasks), and the importance in defining and implementing annotation tasks for data collection.
